### 2020-08-10 CILAMCE_2020/paper.tex
Minor fixes and make visualiation plots to list

Compressive strength is the main characteristic of concrete, measured by tests of international standards that consist of the breaking of specimens \cite{Gambhir1990}. Measurement at 28 days is mandatory and represents the grade of the concrete. Knowing in advance what the result will be obtained for a given age, based on the proportions of its ingredients, is of great interest to concrete manufacturers, construction companies, and civil engineers.

The compressive strength is a nonlinear function of its ingredients and age, making it difficult to establish an analytical formula, although some formulas have already been proposed by \citet{Hasan2011} and  \citet{Kabir2012}. However, most of the studies have build models including the age as a feature along with the ingredients, but due to the non linearity between the compressive strength and age, we have find the need of further investigation of models that separate the age and analyse only the ingredients, then specify for each age.

@@

% \citet{Hasan2011} proposed a mathematical model to predict 28 day compressive strength from the results of tests of 7 and 14 days, and \citet{Kabir2012} from 7 days. These are analytical formulas, but use

%  This set of samples is so well known that there are many pages on the internet of unpublished studies that use it and have good results, such as \citet{Abban2016}, \citet{Raj2018}, \citet{Modukuru2020} and \citet{Pierobon2018}. Later in this paper all studies are compared with the results found here.

@@

\citet{Alshamiri2020} proposed a new Regularized Extreme Learning Machine (RELM) method to train Artificial Neural Networks models to predict the compressive strenght. The results were compared with several known algorithms running on the same dataset, including individual and essembles, and the proposed model had the best result by far.

@@

Several plots and tables were built to perform the exploration and visualization of the samples prepared in the previous step. Including analysis of the descriptive statistics of the continuous and categorical variables, the distribution of the variables in relation to the compressive strength, the correlation between the variables grouped by age, the relationship between the approximate mix and the compressive strength, the relationships between the main concrete ingredients and the compressive strength and principal component analysis (PCA) of the ingredients.

@@

Six different models were built, one for each age-set, the following steps were made for each one:

>>>>

Compressive strength is the main characteristic of concrete, measured by tests of international standards that consist of breaking of specimens \cite{Gambhir1990}. Measurement when the concrete is 28 days old is mandatory and represents the grade of the concrete. Knowing in advance the result for a given age, based on the proportions of its ingredients, is of great interest to concrete manufacturers, construction companies, and civil engineers.

The compressive strength is a nonlinear function of its ingredients and age, making it difficult to establish an analytical formula, although some formulas have already been proposed by \citet{Hasan2011} and  \citet{Kabir2012}. However, most of the studies have built models including the age as a feature along with the ingredients, but due to the non linearity between the compressive strength and age, we have found the need of further investigation of models that separate the age and analyse only the ingredients, then specify for each age.

@@

@@

\citet{Alshamiri2020} proposed a new Regularized Extreme Learning Machine (RELM) method to train Artificial Neural Networks models to predict the compressive strenght. The results were compared with several known algorithms running on the same dataset, including individual and ensembles, and the proposed model had the best result by far.

@@

In addition to the already presented plots, several other plots and tables were built to perform the exploration and visualization of the samples prepared in the previous step, including:

\begin{itemize}

\item Analysis of the descriptive statistics of the continuous and categorical variables;

\item Distribution of the variables in relation to the compressive strength;

\item Correlation between the variables grouped by age;

\item Relationship between the approximate mix and the compressive strength;

\item Relationship between the main concrete ingredients and the compressive strength;

\item Principal component analysis (PCA) of the ingredients.

\end{itemize}

@@

Six different models were built, one for each age-set, and the following steps were made for each one:
